Exploring Design Space for Differentially Private Bayesian Inference

### 2019-01-05 ICML2019/main.tex
update mechanisms

\subsection{Exponential Mechanism Family}
In this section, we explore the exponential mechanism family: $\expmech(\cdot,\cdot,\cdot)$ by considering Hellinger distance metrics and different sensitivities.

Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set as candidate set where the mechanisms in this family sample from:

\[
  \candidateset\equiv\{\bysinfer(binomial(\theta), \bprior,\dataobs)\mid \dataobs \in \{0,1\}^n\}.
\]
For simplicity:
\[
  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha\}
\]
over all $\dataobs \in \{0,1\}^n$, where $\Delta\alpha$ is as defined in Section \ref{sec_background}, and
\[
  \candidateset\equiv\{\dirichlet(\valpha')\mid \valpha'=\valpha + \Delta\valpha\},
\]
over all $\dataobs \in \mathcal{X}^n$ in Dirichlet-multinomial model.

We don't explicitly
parametrize the result by the prior and likelihood, which from now on we consider
fixed and we denote them by $\bprior$ and $binomial(\theta)$, $multinomial(\theta)$. We use $\bysinfer(\dataobs)$ to denote the Bayesian inference process when the other two parameters are fixed.

\subsubsection{Standard Exponential Mechanism with Hellinger Metric}
Standard exponential mechanism $\expmech(x,u,\candidateset)$ samples an element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
\begin{equation*}
\underset{z \thicksim \expmech(x,u,\candidateset) }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\end{equation*}
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e. the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

Exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.

\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$ share the same candidate set and utility function as it with standard exponential mechanism. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\end{equation*}

where $LS(\dataobs)$ is the local sensitivity of scoring function, calculated by:

\begin{equation*}
LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
\end{equation*}

The exponential mechanism with local sensitivity is non-differential privacy\cite{dwork2014algorithmic}.

\subsubsection{Exponential Mechanism with Hellinger Metric and Smoothed Sensitivity}
\label{subsec_hexpmech}

\begin{definition}
\label{def_gamma_smooth}
Given data set $\dataobs$ of size $n$, we define $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ is:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{definition}

@@

\begin{proof}
of Theorem. \ref{thm_gamma_smooth}.

For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:

By Equation (\ref{eq_smooth}):
\begin{equation*}
\begin{split}
S(\dataobs) 
& = \max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \}\\
\frac{1}{S(\dataobs)} 
& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
\end{split}
\end{equation*}

@@

\begin{equation*}
\begin{split}
& \leq \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{  \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs'')) \bigg \}\\
& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
\gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
\}\\
& = \gamma + \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
\}\\
& = \gamma + \frac{1}{S(\dataobs')}
\end{split}
\end{equation*}
$\implies$
\begin{equation*}
\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.
\end{equation*}

\begin{definition}
\label{def_smoo_2}
$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
{\unomalizer{\dataobs}}.
\end{equation*}
where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Definition \ref{def_gamma_smooth} by setting $\gamma = 1$.
\end{definition}

Mechanisms in Exponential mechanism family also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-multinomial system.

@@

% \subsection{Privacy Analysis for Baseline Mechanisms}
% In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}. The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.
\subsection{Privacy of Laplace Mechanism Family}
Mechanisms in Laplace family are $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.

@@

\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $\epsilon$-differential privacy.
\end{lem}
\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.

  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:

  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
  \begin{equation*}
  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
  \end{equation*}

  By definition \ref{def_smoo_2}:
  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \\
  & \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}
  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot \exp\big( \frac{\epsilon}{4} \big) \\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  & \cdot \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)\\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  & \cdot \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

@@

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{4}$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)}\\
  & \cdot\frac{1}{
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }
  \end{split}
  \end{equation*}

@@

  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved.

>>>>

\subsection{Exponential Mechanism Family}
In this section, we explore the exponential mechanism family: $\expmech$ by considering Hellinger distance metrics and different sensitivities.\\
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and an observed data set: $\dataobs\in\{0,1\}^n$, we define the follwing set as candidate set where the mechanisms in this family sample from:
\[
  \candidateset\equiv\{\bysinfer(\binomial{n}{\theta}, \bprior,\dataobs')\mid \dataobs' \in \{0,1\}^n\}.
\]
For simplicity:
$
  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha + \Delta\alpha, \beta'=\beta + n-\Delta\alpha\}
$
over all $\dataobs \in \{0,1\}^n$, where $\Delta\alpha$ is as defined in Section \ref{sec_background}, and
$
  \candidateset\equiv\{\dirichlet{\valpha'} \mid \valpha'=\valpha + \Delta\valpha\}
$,
over all $\dataobs \in \mathcal{X}^n$ in Dirichlet-multinomial model.\\
We use $\bysinfer(\dataobs)$ to denote the Bayesian inference process when the other two parameters are fixed, denoted by $\bprior$ and $\binomial{n}{\theta}$, $\multinomial{n}{\vtheta}$.

\subsubsection{Standard Exponential Mechanism with Hellinger Metric}
Our exploration starts from the standard exponential mechanism $\expmech(x,u,\candidateset)$, which samples an element from the candidate set $\candidateset$ with probability proportional to $\exp(\frac{\epsilon u(x,r)}{2 GS})$:
\[
\underset{z \thicksim \expmech(x,u,\candidateset) }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\]
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity of the scoring function (i.e. the global sensitivity of the Bayesian inference w.r.t the Hellinger distance), calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

\subsubsection{Exponential Mechanism with Hellinger Metric and Local Sensitivity}
\label{subsec_emls}
In order to achieve good accuracy, we make an attempt on the Exponential mechanism with local sensitivity $\lexpmech(x,u,\candidateset)$. This is just an attempt since local sensitivity is non-private. $\lexpmech$ shares the same candidate set and utility function as $\expmech$, outputting a result $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\[
\underset{z \thicksim \lexpmech(x,u,\candidateset)}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\]
where $LS(\dataobs)$ is the local sensitivity of scoring function, calculated by:
\begin{equation*}
LS(\dataobs)=\max_{\dataobs' \in \datauni^n: \\ \adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
\end{equation*}

\subsubsection{Exponential Mechanism with Hellinger Metric and Smoothed Sensitivity}
\label{subsec_hexpmech}
In this section, we explore a new mechanism in Exponential family, which can achieve good accuracy and differential privacy simultaneously, by scaling the noise to a new sensitivity. We first define the new sensitivity we are going to use and then present the mechanism.
\begin{definition}
\label{def_gamma_smooth}
Given data set $\dataobs$ of size $n$, we define $\gamma -$smooth sensitivity of Bayesian inference process w.r.t. the Hellinger distance $S(\dataobs)$ is:
\begin{equation}
  \label{eq_smooth}
   S(\dataobs)=\max_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'')} \bigg \},
\end{equation}
where $d$ is the Hamming distance between two data sets.
\end{definition}

@@

\begin{proof}
of Theorem. \ref{thm_gamma_smooth}.\\
For $\adj{\dataobs}{\dataobs'}$ and arbitrary $\dataobs'' \in \{0,1\}^{n}$:\\
From Equation (\ref{eq_smooth}), we can get:
\[
\frac{1}{S(\dataobs)} 
 = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{ \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs,\dataobs'') \bigg \}\\
\]

@@

\begin{equation*}
\begin{split}
& \leq \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{  \frac{1}{LS(\dataobs'')} +\gamma \cdot (1 + d(\dataobs',\dataobs'')) \bigg \}\\
& = \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
\gamma + \frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg 
\}\\
& = \gamma + \min_{\dataobs'' \in \{0,1\}^{n}}\bigg \{
\frac{1}{LS(\dataobs'')} +\gamma \cdot d(\dataobs',\dataobs'')\bigg
\}\\
& = \gamma + \frac{1}{S(\dataobs')}
\end{split}
\end{equation*}
Then we can get:
$\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma.$
\end{proof}

\begin{definition}
\label{def_smoo_2}
$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
{\unomalizer{\dataobs}}.
\end{equation*}
where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Definition \ref{def_gamma_smooth} by setting $\gamma = 1$.
\end{definition}
Mechanisms in Exponential mechanism family also extends to the Dirichlet-multinomial system $\dirichlet{\valpha}$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet{\valpha_1}, \dirichlet{\valpha_2}) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{thm_gamma_smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-multinomial system.

@@

\subsection{Privacy of Laplace Mechanism Family}
Mechanisms in Laplace family are $\epsilon-$differential privacy by \cite{dwork2014algorithmic}.

@@

\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $\epsilon$-differential privacy.
\end{lem}
\begin{proof} of Lemma \ref{lem_hexpmech_privacy}.\\
  By Definition \ref{def_epsilon_dp}, to proof Lemma \ref{lem_hexpmech_privacy}, we need to prove:\\
  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
  \begin{equation*}
  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
  \end{equation*}
  By definition \ref{def_smoo_2}:
  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {\exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {\exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \\
  & \cdot \exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}
  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot \exp\big( \frac{\epsilon}{4} \big) \\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  & \cdot \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)\\
  & = \exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  & \cdot \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

@@

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{4}$:
  \begin{equation*}
  \begin{split}
  & \leq \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  }\\
  & \cdot 
  \frac{1}
  {
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  }\\
  & = \exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  \exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  \exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)}\\
  & \cdot\frac{1}{
  \exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  \exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }
  \end{split}
  \end{equation*}

@@

  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved by $\hexpmech$.
